Aluffi


Chapter I)

Section 1)

1.1) In a nutshell, Russell's paradox proves, by contradiction, that certain mathematical collections cannot be sets. It posits the existence of a "set of all sets that don't contain themselves". Such a set can neither contain itself (since in that case, it would be a "set that does contain itself", and should be excluded); nor can it exclude it itself (since in that case, it would be a "set that doesn't contain itself", and should be included).



1.2) Prove that any equivalence relation over a set $S$ defines a partition of $\mathcal{P}_S$.

a) $\mathcal{P}_S$ has no empty elements: any element in $S$ is part of at least one equivalence class, the class containing at least that element itself. Since there is no equivalence class constructed independently from elements, there are no empty equivalence classes.

b) Elements of $\mathcal{P}_S$ are disjoint: suppose there is an element $x$ that is part of $A$ and $B$, two distinct equivalence classes. $\forall a \in A, x \sim a$ and $\forall b \in B, x \sim b$. By transivity through $x$, $\forall a \in A, \forall b \in B, a \sim b$. Therefore, $A$ and $B$ are the same equivalence class: $A = B$. Contradiction. Therefore all elements of $\mathcal{P}_S$ are disjoint subsets of $S$.

c) The union of all elements of $\mathcal{P}_S$ makes up $S$: suppose $\exists x \in S$ such that $x \notin \bigcup_{S_i \in \mathcal{P}_S} S_i$. From the argument made in (a), $x$ exists in at least one equivalence class, the class which contains only $x$ itself. This is one of ou $S_i$ sets. Contradiction. Therefore, $\bigcup_{S_i \in \mathcal{P}_S} S_i = S$



1.3) Given a partition $\mathcal{P}$ on a set $S$, show how to deﬁne a relation $\sim$ on $S$ such that $P$ is the corresponding partition.

The insight here is to build an equivalence relation such that two elements are equivalent if and only if they are part of the same subset of $S$, which is understood as their common equivalence class.

We define $\sim$ such that $\forall S_i, S_j \in \mathcal{P}, \forall x \in S_i, \forall y \in S_j, x \sim y \Leftrightarrow S_i = S_j$.

Let us prove that $\sim$ is an equivalence relation.

a) Reflexivity: $\forall A \in \mathcal{P}, \forall x \in A, A = A \Rightarrow x \sim x$

b) Symmetry: $\forall S_i, S_j \in \mathcal{P}, \forall x \in S_i, \forall y \in S_j, x \sim y \Leftrightarrow S_i = S_j \Leftrightarrow S_j = S_i \Leftrightarrow y \sim x$

c) Transitivity: $\forall S_i, S_j, S_k \in \mathcal{P}, \forall x \in S_i, \forall y \in S_j, \forall z \in S_k, x \sim y \cap y \sim z \Leftrightarrow S_i = S_j \cap S_j = S_k \Rightarrow S_i = S_k \Leftrightarrow x \sim z$

Therefore, $\sim$ is indeed an equivalence relation, and is generated uniquely by the partition.



1.4) How many different equivalence relations may be deﬁned on the set $\{1, 2, 3\}$?

If we start with the 1 element set, we have only one possible partition, one possible equivalence class.

With the 2 element set, there are 2 partitions, $\{\{1, 2\}\}$ and $\{\{1\}, \{2\}\}$.

With the 3 element set, there is:
- 1 partition of type 1-1-1: $\{\{1\}, \{2\}, \{3\}\}$.
- 3 partitions of type 2-1: $\{\{1\}, \{2, 3\}\}$, $\{\{2\}, \{1, 3\}\}$, and $\{\{3\}, \{1, 2\}\}$.
- 1 partition of type 3: $\{\{1, 2, 3\}\}$.

Hence, there are five equivalence classes on the 3 element set.

See the Bell numbers: https://oeis.org/A000110



1.5) Give an example of a relation that is reﬂexive and symmetric, but not transitive. What happens if you attempt to use this relation to deﬁne a partition on the set?

In terms of graph theory, if we express a set with an internal relation as a graph, we can represent elements are nodes and relationships are edges. Reflexivity means that every node has a loop (unary, self-edge). Symmetry means that the graph is not directed (since every relationship goes both ways). Transitivity means that every connected subset of nodes is a maximal clique (synonymously, every connected component is a complete subgraph).

In a relation which is reflexive and symmetric, but not transitive, you would have connected components of this graph which are not cliques. For these, there is ambiguity as to how you would group their nodes. Two obvious choices would be either:

- to remove the minimal number of edges to obtain n distinct cliques (thereby gaining the transitive restriction of the relation) from a given non-clique;

- to complete the connected subgraph into a clique (thereby gaining the transitive closure of the relation).



1.6) Deﬁne a relation $\sim$ on the set $\mathbb{R}$ of real numbers, by setting $a \sim b \Leftrightarrow b - a \in \mathbb{Z}$. Prove that this is an equivalence relation, and ﬁnd a 'compelling' description for $\mathbb{R}/\sim$. Do the same for the relation \approx on the plane $\mathbb{R} \times \mathbb{R}$ deﬁned by declaring $(a_1, a_2) \approx (b_1, b_2) \Leftrightarrow b_1 - a_1 \in \mathbb{Z} \text{ and } b_2 - a_2 \in \mathbb{Z}$.

$b - a \in \mathbb{Z}$ means that 2 real numbers differ by an integral amount. This means that the equivalence relation algebraically describes the idea that "with this relation, 2 real numbers are the same iff they have the same fractional component $x$ (or $1 - x$ for negative numbers)". Eg, $4.76 \sim 1024.76 \sim -5.34$, since $-5.34 + 10 = 4.76$, etc.

To make an algebraic quotient of a set by an equivalence relation, we take the function which maps each element to its corresponding equivalence class, in the set (partition) containing these equivalence class. Intuitively, this is similar to keeping only one representative element per equivalence class. For the example class above, we can keep the representative $0.76$. There is such an equivalence class for every fractional part possible, that is, one for every number in $[0, 1[$. The corresponding map is the "real remainder of division modulo 1". This map is well-defined because each real number has only one output for this map, and all real numbers that are equivalent through $\sim$ are mapped to the same value in the output set.

We should also notice that since $0 \sim 1$, this space loops around on itself. Intuitively, if you increase linearly in the input space $\mathbb{R}$, it goes back to $0$ after $0.9999999...$ in the output space. This output space is thus a circle of perimeter $1$.

Similarly, $b_1 - a_1 \in \mathbb{Z} \text{ and } b_2 - a_2 \in \mathbb{Z}$ means that 2 points in the 2D plane are the same iff they differ in each coordinate by an integral amount. This boils down to combining two such loops from the first part of the exercise: one in the $x$ direction and one in the $y$ direction: what this gives is the small square $[0, 1[ \times [0, 1[$, which loops to $x = 0$ (resp. $y = 0$) when $x = 1$ (resp. $y = 1$) is reached. This space functions like a small torus, of area $1$.





Section 2)

2.1) How many different bijections are there between a set $S$ with $n$ elements and itself?

Any bijection is a choice of a pairs from 2 sets of the same size, where each element is used only once, and each pair has one element from each set. At first there are n choices in each set. If we pick a pair, we pick from $n^2$ possibilities 

There are then $(n-1)^2$ choices of pairs left, etc.

Ccl°: $\prod_{i=1}^{i=n} i^2 = (n!)^2$



2.2) Prove that a function has a right-inverse iff it is surjective (can use AC)

Let $f \in (A \to B)$.

2.2.a) $\Rightarrow$: Suppose that $f$ has a right-inverse (pre-inverse).
We have $\exists g \in (B \to A), f \circ g = id_B$

Suppose that $f$ is not a a surjection. This means $\exists b \in B, \nexists a \in A, b = f(a)$

$f(g(b))= id_B (b) = b$ Necessarily, $g(b)$ is such an $a$, so $\exists a \in A, b = f(a)$. Contradiction.

Ccl°:: f is a surjection.

2.2.b) $\Leftarrow$: Suppose that f is a surjection.

$\forall b \in B, \exists a \in A, b = f(a)$

We will construct a pre-inverse for $f$.

The insight here is to realize that a surjection divides its input set into a partition, where each 2-by-2 disjoint subset corresponds to $f^{-1}(\{q\})$, for every $q$ in the output set. More formally, each "fiber" (preimage of a singleton) is a disjoint subset of the input set, and the union of fibers is the input set itself. You can see this in the following diagram:

(add diagram)
1234 to ab
1a 2a (fiber from a)
3b 4b (fiber from b)
https://tex.stackexchange.com/questions/157450/producing-a-diagram-showing-relations-between-sets
https://tex.stackexchange.com/questions/79009/drawing-the-mapping-of-elements-for-sets-in-latex

Using AC, we select a single element from each such fiber. For each $q \in B$, we name $p_q \in f^{-1}(\{q\})$ the chosen element. We define $g$ as $g \in (B \to A), g = (q \mapsto p_q)$. With this, $\forall b \in B, f \circ g (b) = b$, and so $f \circ g = id_A$. Thus, $f$ has a preinverse.

A summary of this idea: all surjection preinverses are simply a choice of a representative for each fiber of the surjection as the output to the respective singleton.



2.3) Prove that the inverse of a bijection is a bijection, and that the composition
of two bijections is a bijection.

2.3.a) Using the fact that a function is a bijection iff it has a two-sided inverse (Corollary 2.2), we can see from this defining fact, $f \in (A \to B) \text{bijective } \Leftrightarrow, \exists f^{-1} \in (B \to A), f^{-1} \circ f = id_A \text { and } f \circ f^{-1} = id_B$ that $f$ is naturally $f^{-1}$'s (unique) two-sided inverse, and so $f^{-1}$ is also a bijection.

2.3.b) Let be $f \in (A \to B), g \in (B \to C)$, both bijective (hence with inverses in the respective function spaces). Let $h \in (A \to C), h = g \circ f$ and $h^{-1} \in (C \to A), h^{-1} = f^{-1} \circ g^{-1}$. We have:

$$
\begin{align*}
h^{-1} \circ h &= (f^{-1} \circ g^{-1}) \circ (g \circ f) \\
               &=  f^{-1} \circ g^{-1}  \circ  g \circ f  \\
               &=  f^{-1} \circ          id_B    \circ f  \\
               &=  f^{-1} \circ                        f  \\
               &=  id_A
\end{align*}
$$

$$
\begin{align*}
h \circ h^{-1} &= (g \circ f) \circ (f^{-1} \circ g^{-1}) \\
               &=  g \circ f  \circ  f^{-1} \circ g^{-1}  \\
               &=  g \circ     id_B         \circ g^{-1}  \\
               &=  g \circ                        g^{-1}  \\
               &=  id_C
\end{align*}
$$

Therefore $h$ and $h^{-1}$ are two-sided inverses of each other, and thus bijections. From this we conclude that the composition of any two bijections is also a bijection.



2.4) Prove that ‘isomorphism’ is an equivalence relation (on any set of sets).

2.4.a) Problem statement

Let $\mathcal{A}$ be a set of sets. We define the relation $\simeq$ between the elements of $\mathcal{A}$ as the following:

$$\forall X, Y \in \mathcal{A}, \; X \simeq Y \Leftrightarrow \text {there exists a bijection between $X$ and $Y$}$$

Let us show that $\simeq$ is an equivalence relation.


2.4.b) Reflexivity

For any set $A \in \mathcal{A}$, the identity mapping on $A$ is a bijection. This means that $\forall A \in \mathcal{A}, A \simeq A$, ie, $\simeq$ is reflexive.


2.4.c) Symmetry

$$
\begin{align*}
\forall X, Y \in \mathcal{A}, \; X \simeq Y & \Rightarrow \exists f      \in (X \to Y) \text{ bijective} \\
                                            & \Rightarrow \exists f^{-1} \in (Y \to X) \text{ bijective} \\
                                            & \Rightarrow Y \simeq X
\end{align*}
$$

Therefore, $\simeq$ is symmetric.


2.4.d) Transitivity

Let be $X, Y, Z \in \mathcal{A}$.
Suppose that $X \simeq Y$ and $Y \simeq Z$.
This means $\exists f \in (X \to Y), g \in (Y \to Z)$, both bijections.
Let be $h \in (X \to Z), h = g \circ f$. $h$ is also a bijection since the composition of two bijections is also a bijection (exercise 2.3).
The existence of $h$ implies $X \simeq Z$.

Therefore $\simeq$ is transitive.


2.4.e) Conclusion

Isomorphism, $\simeq$, is a relation on an arbitrary set (of sets) which is always reflexive, symmetric and transitive. It is thus an equivalence relation



2.5) Formulate a notion of epimorphism and prove that epimorphisms and surjections are equivalent.

See "notes" file: section "Proofs of mono/inj and epi/surj equivalence".


2.6) With notation as in Example 2.4, explain how any function $f \in (A \to B)$ determines a section of $\pi_A$.

A section is the preinverse of a surjection. Here, the surjection in question is $\pi_A$ the projection of $A \times B$ onto $A$.

Let $f \in (A \to B)$.

% We remind that all functions are technically themselves sets, more precisely, they are relations between pairs of sets, hence $(A \to B) \subseteq (A \times B)$. We first define the map $\iota \in ((A \to B) \to (A \times B)), \; \iota = (f \mapsto \Gamma_f)$, which canonically injects a function from the function space $(A \to B)$ into the cartesian product $(A \times B)$, by simply keeping every pair $(a, f(a))$ as-is. $\Gamma_f$ is the \textit{graph} or \textit{graphical representation} of $f$.

We now consider the function which maps an input $a \in A$ of $f$ to its "geometric representation" (its coordinates in the enclosing space $A \times B$, corresponding to a point of the graph $\Gamma_f$). 
$$\hat{f} \in (A \to (A \times B)), \hat{f} = ( \; a \mapsto (a, f(a)) \; )$$
We notice that $\hat{f}(A) = \Gamma_f$.

Naturally, $\pi_A \circ \hat{f} = (a \mapsto a) = id_A$, therefore, $\hat{f}$ is a pre-inverse (section) of $\pi_A$.

This set of relationships can be expressed in the following commutative diagram:

% incorrect because of iota's nature; shifting rank (sets of sets to simple sets) is a bad idea
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZARgBoAGAXVJADcBDAGwFcYkQAdDgIxgHMsYYAFt6OAE5YAHgF8AggAIueYfAUAKRcogKAQgEolXDhvqkFAM31cYYKCLGTZIGaXSZc+QinKli1OiZWdi5eASFRCWkZBS1jBXojW3tIpxkXNxAMbDwCIgAmPwCGFjZETh5+QQco2Q04nB0DIy5LJLsatIz3HK8iMnzioLKKsOrU6K4AcXphUQB9CyM4Zm44GBx6oxU1ZuMTdTNLQ-1DGw6J5xkAmCg+eCJQC3EIYSRfEEakMkDS9jR5nIQDRGPReIwAAoeXLeECSPgACxwwJACJg9Cg7BwAHcIGiMQhXE8Xm9EB8vohCr9guUAcBNNsmvp0iCwTBIdC+uVGDALMiaPjMeUcXj0VBCZlnq9vjQKQBmGglGkVBFiYAWFkgUHgqG9PLleFIlE4ehYRjsBEQCAAaxRcARWD5MpAvDs7yJIClpKp8sVwxCHHwJpR2vZus8+q1vP5qLFSDAzEYjFlpvN5UtNu6npJSAVnwgzqVIy4aCwgJDbI5ethhpjgqxuMFCBo9sdyMQxGuMiAA
% \begin{tikzcd}
%                                                                              & {\begin{matrix}A \times (A \to B) \\ (a, f)\end{matrix}} \arrow[ld, "p_A"', two heads] \arrow[rd, "p_{(A \to B)}", two heads] &                                                                      \\
% \begin{matrix} A \\ a \end{matrix} \arrow[rd, "\hat{f}"', hook, shift right] &                                                                                                                               & \begin{matrix} (A \to B) \\ f \end{matrix} \arrow[ld, "\iota", hook] \\
%                                                                              & {\begin{matrix}\Gamma_f \subseteq (A \times B) \\ (a, f(a)) \end{matrix}} \arrow[lu, "\pi_A"', two heads, shift right]          &                                                                     
% \end{tikzcd}
%Where $p_A$ and $p_B$ are the appropriate left and right projectors for the corresponding space.


%this one is much simpler and neater
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZARgBoAGAXVJADcBDAGwFcYkQAdDgIxgHMsYYAFt6OAE5YAHgF8ABFwDi9YaID6AMwUc4zbnBg45AQW15h8OQCFtXOQAp6pORscBKN9phgoIsZNkQGVJ0TFx8QhRyUmJqOiZWdi5eASFRCWl5Uy47ei8fPwzA4NDsPAIiACYYuIYWNkROHn5BQoD5GxyOF3d833T2oLiYKD54IlANcQhhJDIQHAgkaPj6pI4ACzFgDRkQGjgNrA0cJABaeZx6LEZ2DYgIAGsgkJApmeWaRbmDo5Pz+YbGD0KDsHAAdwgQJBCBodUSjS4aCwamML0m01miEuS0Q1VWCLe+xAjHovEYAAUwuVIiBJHwNqcSm9MZ8Frj8dDQY0IVDgVBYSBDsdTni4QkGk1kWorEMZEA
\begin{tikzcd}
                                                                                            & {\begin{matrix} \Gamma_f \subseteq A \times B \\ (a, f(a)) \end{matrix}} \arrow[ld, "\pi_A", two heads, shift left] \arrow[rd, "\pi_B", two heads, shift right=2] &                                       \\
\begin{matrix} A \\ a \end{matrix} \arrow[ru, "\hat{f}", hook, shift left] \arrow[rr, "f"'] &                                                                                                                                                                 & \begin{matrix} B \\ f(a) \end{matrix}
\end{tikzcd}



PS: see "On sections and fibers" in the "notes" file for a worked example.



2.7) Let $f = (A \to B)$ be any function. Prove that the graph $\Gamma_f$ of $f$ is isomorphic to $A$.

Using the elements from the previous exercise, we know that $\hat{f}$ is injective from $A$ into $A \times B$. This property is inherited to any restriction of the codomain $Z \subseteq B$, and corresponding implied restriction of the domain to $Y = f^{-1}(Z) \subseteq A$. In particular, here, $Y = A$ and $Z = \Gamma_f = \hat{f}(A)$. We now consider $\overline{f} \in (A \to \Gamma_f), \overline{f} = (a \mapsto \hat{f}(a))$. We can see that $\overline{f}$ is injective from being a restriction of an injective function to a smaller codomain. We also know that $\overline{f}$ is surjective, since its domain is its image. Therefore, $\overline{f}$ is a bijection. This means that $A \simeq \Gamma_f$.



2.8) Describe as explicitly as you can all terms in the canonical decomposition of the function $f \in (\mathbb{R} \to \mathbb{C})$ deﬁned by $f = (r \mapsto e^{2 \pi i r})$. (This exercise matches one assigned previously, which one?)

Firstly, elements of $\mathbb{R}$ are equivalent by this map (they have the same output) if they vary by $1$ from each other. This is a reference to the equivalence relation $\sim$ in exercise 1.6. Therefore, we will use $\mathbb{R}/\sim \simeq S^1$ in our decomposition. Obviously, the map from $(\mathbb{R} \to \mathbb{R}/\sim)$, which maps each element of $\mathbb{R}$ to respective their equivalence class is a surjection (since there's no empty equivalence class).

Secondly, as mentioned, we have a bijection $\tilde{f}$ between $\mathbb{R}/\sim$ and $S^1$, the circle group of unit complex numbers, namely $\tilde{f} = (x \mapsto e^{2 \pi i x}$, where each element $x$ of $\mathbb{R}/\sim$ can be understood to correspond to a (class representative) value in the interval $[0, 1[$.

Finally, we do the canonical injection of $S^1$ into its superset $\mathbb{C}$.



2.9) Show that if $A \simeq A'$ and $B \simeq B'$ , and further $A \cap B = \emptyset$ and $A' \cap B' = \emptyset$, then $A \cup B \simeq A' \cup B'$. Conclude that the operation $A \coprod B$ (as described in §1.4) is well-deﬁned up to isomorphism.

We suppose the aforementioned.

Let $f_A$ be a bijection from $A \to A'$, and $f_B$ be a bijection from $B \to B'$.

We define the following:

$$
f \in (A \cup B \to A' \cup B'),
\text{ such that }
\begin{cases}
	\forall a \in A, \; f(a) = f_A(a) \\
	\forall b \in B, \; f(b) = f_B(b)
\end{cases}
$$

This function is a well-defined function, since $A \cap B = \emptyset$: every element of the domain has one, and only one, possible image.

Similarly, we define:

$$
g \in (A' \cup B' \to A \cup B),
\text{ such that }
\begin{cases}
	\forall a \in A', \; g(a) = f_A^{-1}(a) \\
	\forall b \in B', \; g(b) = f_B^{-1}(b)
\end{cases}
$$

Similarly, because $A' \cap B' = \emptyset$, $g$ is well-defined.

Let us study $g \circ f$. We have:
$$
\begin{cases}
	\forall a \in A, \; g(f(a)) = f_A^{-1}(f_A(a)) = a \\
	\forall b \in B, \; g(f(b)) = f_B^{-1}(f_B(b)) = b
\end{cases}
$$

Hence, $g \circ f = id_{A \cup B}$.
Similarly, $f \circ g = id_{A' \cup B'}$.
Therefore, $g = f^{-1}$, $f$ is a bijection, and $A \cup B \simeq A' \cup B'$.

We'll now do a shift in notation. Let be some arbitrary sets $A$ and $B$. Let be $A_1, A_2, B_1, B_2$ such that $A_1 = \{ 1 \} \times A$, $A_2 = \{ 2 \} \times A$, $B_1 = \{ 1 \} \times B$, and $B_2 = \{ 2 \} \times B$. This means $A \simeq A_1$, $A \simeq A_2$, $B \simeq B_1$, and $B \simeq B_2$. It also means $A_1 \cap A_2 = \emptyset$ and $B_1 \cap B_2 = \emptyset$. From the above, this implies $A_1 \cup B_1 \simeq A_2 \cup B_2$.

This means that the disjoint union of $A$ and $B$ is indeed well-defined, up to isomorphism: so long as 2 respective copies of $A$ and $B$ are made in a way that their intersection is empty, the 2 respective unions of 1 copy each will be isomorphic.



2.10) Show that if $A$ and $B$ are ﬁnite sets, then $|B^A| = |B|^{|A|}$.

The number of $|B^A|$ functions in $B^A = (A \to B)$ can be counted in the following way.

For each element $a$ of $A$, of which there are $|A|$, we can pick any element of $|B|$ as the image. This means $|B| \times ... \times |B|$, a total of $|A|$ times. Hence, $|B^A| = |B|^{|A|}$.



2.11) In view of Exercise 2.10, it is not unreasonable to use $2^A$ to denote the set of functions from an arbitrary set $A$ to a set with $2$ elements (say $\mathbb{B} = \{0, 1\}$). Prove that there is a bijection between $2^A$ and the power set $\mathcal{P}(A)$ of $A$.

Simply put, every subset $A_i$ of $A$ is built through a series of $|A|$ choices: for each element $a$ in $A$, do we keep the element $a$ in our subset $A_i$ (output $1$) or do we remove it (output $0$) ? It is then easy to see that such a series of choices can easily be encoded as a unique function in $A \to \mathbb{B}$. The totality of such series of choices thus corresponds both to the space $A \to \mathbb{B}$, and to the powerset $\mathcal{A}$, and there is a bijection between the two. 





Section 3)

3.1) Let $\mathcal{C}$ be a category. Consider a structure $\mathcal{C}^{op}$ with:
 - $Obj(\mathcal{C}^{op}) \coloneqq Obj(\mathcal{C})$;
 - for $A$, $B$ objects of $\mathcal{C}^{op}$ (hence, objects of $\mathcal{C}$), $Hom_{\mathcal{C}^{op}} (A, B) \coloneqq Hom_{\mathcal{C}} (B, A)$
Show how to make this into a category.

3.1.a) Composition

First, to make things clearer and more rigorous, let us distinguish composition in $\mathcal{C}$ as $\circ$ and composition in $\mathcal{C}^{op}$ as $\star$. We define $\star$ as:
$$
\begin{align*}
	& \forall f \in Hom_{\mathcal{C}^{op}} (B, A) = Hom_{\mathcal{C}} (A, B), \\
	& \forall g \in Hom_{\mathcal{C}^{op}} (C, B) = Hom_{\mathcal{C}} (B, C), \\
	& \exists h \in Hom_{\mathcal{C}^{op}} (C, A) = Hom_{\mathcal{C}} (A, C), \\
	& f \star g \coloneqq g \circ f = h
\end{align*}
$$

We will now show that $\mathcal{C}^{op}$ with $\star$ verifies the other axioms of a category (namely identity and assossiativity of composition).

3.1.b) Identity

Since $\mathcal{C}$ is a category, since $\mathcal{C}^{op}$ has the same objects, and since, by definition, for all object $A$, we have $Hom_{\mathcal{C}^{op}} (A, A) = Hom_{\mathcal{C}} (A, A)$, we can take every $id_A \in Hom_{\mathcal{C}}(A, A)$ as the same identity in $\mathcal{C}^{op}$. We can verify that this is compatible with $\star$:

$$
\begin{align*}
	\forall A, B & \in Obj (\mathcal{C})        &=& \;  Obj (\mathcal{C}^{op})        , \\
	\exists id_A & \in Hom_{\mathcal{C}} (A, A) &=& \;  Hom_{\mathcal{C}^{op}} (A, A) , \\
	\exists id_B & \in Hom_{\mathcal{C}} (B, B) &=& \;  Hom_{\mathcal{C}^{op}} (B, B) , \\
	\forall f    & \in Hom_{\mathcal{C}} (A, B) &=& \;  Hom_{\mathcal{C}^{op}} (B, A) , \\
	f            & =   f    \circ id_A          &=& \;  id_A \star f                  , \\
	f            & =   id_B \circ    f          &=& \;  f    \star id_B                 \\
\end{align*}
$$

3.1.c) Associativity

Using associativity in $\mathcal{C}$, we have:

$$
\begin{align*}
	\forall A, B, C, D & \in Obj (\mathcal{C})        &=& \;  Obj (\mathcal{C}^{op})        , \\
	\forall f          & \in Hom_{\mathcal{C}} (A, B) &=& \;  Hom_{\mathcal{C}^{op}} (B, A) , \\
	\forall g          & \in Hom_{\mathcal{C}} (B, C) &=& \;  Hom_{\mathcal{C}^{op}} (C, B) , \\
	\forall h          & \in Hom_{\mathcal{C}} (C, D) &=& \;  Hom_{\mathcal{C}^{op}} (D, C) , \\
\end{align*}
$$
$$
\begin{align*}
	h \star (g \star f) &=&  h \star (f  \circ g) \\
						&=& (f \circ  g) \circ h  \\
						&=&  f \circ  (g \circ h) \\
						&=&  (g \circ h) \star f  \\
						&=&  (h \star g) \star f  \\
\end{align*}
$$

Therefore, $\star$ is associative.

We conclude that $\mathcal{C}^{op}$ is a category.



3.2) If $A$ is a finite set, how large is $End_{\text{Set}}(A)$ ?

We know that, in Set, $End_{\text{Set}}(A) = (A \to A) = A^A$. From a previous exercise, we know that $|B^A| = |B|^|A|$, therefore $|End_{\text{Set}}(A)| = |A|^|A|$.



3.3) Formulate precisely what it means to say that "$1_a$ is an identity with respect to composition" in Example 3.3, and prove this assertion.

Example 3.3 is that of a category over a set $S$ with a (reflexive, transitive) relation $\sim$, where the objects of the category are the elements of $S$, and the homset between two elements $a$ and $b$ is the singleton $(a,b)$ if $a \sim b$, and $\emptyset$ otherwise. Composition $\circ$ is given by transitivity of $\sim$, where $(b,c) \circ (a,b) = (a,c)$. Reflexivity gives the identities ($id_a = (a,a)$ for any element $a$).

In this context, to say that "$1_a$ is an identity with respect to composition" means that we can cancel out an element of the form $(a,a)$ from a composition.

Formally, we have:

$$\forall a,b \in S, (b,b) \circ (a,b) = (a,b) = (a,b) \circ (a,a)$$

proving that $(b,b)$ is indeed a post-identity, and $(a,a)$ a pre-identity, in this context.



3.4) Can we deﬁne a category in the style of Example 3.3, using the relation $<$ on the set $\mathbb{Z}$ ?

(Description of example 3.3 in the exercise 3.3 just above.)

Naively, saying like in example 3.3 "there is a singleton homset $\text{Hom}(a,b)$ each time we have $a < b$", we cannot define such a category, since $<$ is not reflexive, and we would thus lack identity morphisms.

However, in a roundabout way, we can define a category over the \textit{negation} of $<$: "there is a singleton homset $\text{Hom}(a,b)$ each time we DO NOT have $a < b$". Namely this corresponds to the relation $\ge$, which is, itself, reflexive, transitive (and antisymmetric), and is a valid instance of the kind of category presented in example 3.3.

In fact, the pair $(\mathbb{Z}, \geq)$ is an instance of what is called a "totally ordered set", which is a more restrictive kind of "partially ordered set" (also called "poset" for short). Consequently, this kind of category is called a "poset category".



3.5) Explain in what sense Example 3.4 is an instance of the categories considered in Example 3.3.

(Description of example 3.3 in the exercise 3.3 just above.)

Example 3.4 describes a category $\hat{S}$ where the objects are the subsets of a set $S$ (equivalently: elements of the powerset $\mathcal{P}(S)$ of $S$), and morphisms between two subsets $A$ and $B$ of $S$ are singleton (or empty) homsets based on whether the inclusion is true (or false).

Inclusion of sets, $\subset$, is also an order relation, this time between the elements of a set of sets (here, $\mathcal{P}(S)$). This means inclusion is reflexive, transitive, and antisymmetric. This makes $\hat{S}$ a poset category, and thus another instance of example 3.3. 



3.6) Deﬁne a category $V$ by taking $Obj(V) = \mathbb{N}$, and $Hom_V(n, m) = Mat_\mathbb{R}(m, n)$, the set of $m \times n$ matrices with real entries, for all $n, m \in \mathbb{N}$. (I will leave the reader the task to make sense of a matrix with 0 rows or columns.) Use product of matrices to deﬁne composition. Does this
category 'feel' familiar ?

The formulation of the exercise is strange. It says to use the product of matrices to define composition, and to have homsets be sets of matrices, but objects of the category are supposed to be integers. I don't know of any matrix with real entries that maps an integer to an integer in this way.

We thus infer that the meaning of the exercise can be one of two things.

Either we suppose the set of objects could rather be understood as "something isomorphic to $\mathbb{N}$", ie, the collection of real vector spaces with finite bases (ie, $\forall n \in \mathbb{N}, \mathbb{R}^n$). In which case, this is just the category of real vector spaces with finite basis (and linear maps as morphisms), which is a subcategory of the category real vector spaces (commonly called $Vect_{\mathbb{R}}$). In this context, any morphism starting from $0 \simeq \mathbb{R}^0 = \{0\}$ is just the injection of the origin into the codomain; and any morphism ending at $0$ is the mapping of all elements to the origin.

Otherwise, we understand this as "yes, the objects of the category are integers: this means you should ignore the actual content of the matrices, and instead consider only their effect on the dimensionality of domains and codomains". In this case, this category is a complete directed graph over $\mathbb{N}$ where each edge corresponds to the change in dimension (from domain to codomain) caused by a given linear map.



3.7) Deﬁne carefully objects and morphisms in Example 3.7, and draw the diagram corresponding to composition.

Example 3.7 (on coslice categories) refers to example 3.5 (on slice categories). Let's go over slice categories (since example 3.5 asks the reader to "check all [their various properties]").

3.7.1) Slice categories

Slice categories are categories made by singling out an object (say $A$) in some parent (larger) category (say $\mathcal{C}$), and studying all morphisms into that object. These morphisms become the objects of a new category (ie, for any $Z$ of $\mathcal{C}$, $f \in (Z \to A)$ is an object of the slice category, called $\mathcal{C}_A$ in this context). In the slice category, morphisms are defined as those morphism in $\mathcal{C}$ that preserve composition between 2 morphisms into $A$.

Note that there exist pairs of morphisms $f_1 \in (Z_1 \to A)$ and $f_2 \in (Z_2 \to A)$ between which there is no morphism that exists in the slice category. One such example we can make is in $(Vect_\mathbb{R})_{\mathbb{R}^2}$. If we take the maps:

$$f_1 = \begin{bmatrix} 1 & 0 \\ 0 & 0 \end{bmatrix} \in \mathcal{L}(\mathbb{R}^2)$$
$$f_2 = \begin{bmatrix} 0 & 0 \\ 0 & 1 \end{bmatrix} \in \mathcal{L}(\mathbb{R}^2)$$

There exists no map $\sigma$ such that the following diagram commutes (since the output of $f_1$ will always be null in its second coordinate, and the output of $f_2$ will always be null in the first):

% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12BbOnACwBGA4ACUAvgD0ATCDGl0mXPkIoAjOSq1GLNpx78hoyTLkLseAkTKrN9Zq0QduvQcPHTZmmFADm8IqAAZgBOEFxIZCA4EEhS1HY6joEA+qog1Ax0AjAMAAqKFiogwVg+fDiy8iAhYUjqUTGIcVr2bCkmVTXhiJHRdfHaDk7YPjyeYkA
\begin{tikzcd}
\mathbb{R}^2 \arrow[d, "f_1"'] \arrow[r, "\sigma"] & \mathbb{R}^2 \arrow[ld, "f_2"] \\
\mathbb{R}^2                                       &                               
\end{tikzcd}

Now, let us prove that $\mathcal{C}_A$ is indeed a category for an arbitrary object $A$ of an arbitrary category $\mathcal{C}$.

3.7.1.a) Identity

A generic identity morphism is expressed diagrammatically in $\mathcal{C}_A$ as:

% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAC0QBfU9TXfIRQBGclVqMWbTjz7Y8BImWHj6zVohABBbuJhQA5vCKgAZgCcIAWyRkQOCEgBM1NVM2mQ1BnQBGMBgAFfgUhEHMsAwALHG5eEAtrJFF7R0QXCXU2T1kEyxtEOwdk10kNECwoAH0ZeMSCjOL07wgINCVSU0Y4GHEffyCQwTYI6NjSrM1Kqp0uCi4gA
\begin{tikzcd}
Z \arrow[d, "f"'] \arrow[r, "id_Z"]                    & Z \arrow[ld, "f"] \\
A \arrow["id_A"', loop, distance=2em, in=305, out=235] &                  
\end{tikzcd}

We can see that since $f = f \circ id_Z$ in $\mathcal{C}$, this is compatible with the definition of a (pre-/right-)unit morphism in $\mathcal{C}_A$. Also, since the only maps post-$f$ are maps from $A \to A$, we have $id_A$ as the (post-/left-)unit for every morphism $f$ (ie, $f = id_A \circ f$. 

3.7.1.b) Composition

Taking 3 objects of the slice category ($f_1 \in (Z_1 \to A)$, $f_2 \in (Z_2 \to A)$ and $f_3 \in (Z_3 \to A)$), and two morphisms ($\sigma_A$ mapping $f_1$ to $f_2$ via a $\mathcal{C}$-morphism $\sigma \in (Z_1 \to Z_2)$, and $\tau_A$ mapping $f_2$ to $f_3$ via a $\mathcal{C}$-morphism $\tau \in (Z_2 \to Z_3)$), we have that $f_1 = f_2 \circ \sigma$ and $f_2 = f_3 \circ \tau$. This is expressed as the following commutative diagram.

% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAC0B9ARhAF9S6TLnyEU3clVqMWbLgCZ+gkBmx4CReZOr1mrRB04BmJULWiiE7lN2yDAQX5SYUAObwioAGYAnCAFskMhAcCCQJEAY6ACMYBgAFYXUxSJgvHBAdGX0QAB1c7Fd-OlMQXwDw6lCkLWk9NnycOiZS8sDEYOrEIyz6gy8eTMiYuMTzDQMfLFcACwyBbz92iK6eursyzkUFsqWaqrDu3o2Bkz4KPiA
\begin{tikzcd}
Z_1 \arrow[r, "\sigma"] \arrow[rd, "f_1"'] & Z_2 \arrow[r, "\tau"] \arrow[d, "f_2"] & Z_3 \arrow[ld, "f_3"] \\
                                           & A                                      &                      
\end{tikzcd}

Composition of morphisms is then defined as $\tau_A \circ_A \sigma_A$ as a mapping from $f_1$ to $f_3$, such that $f_1 = f_3 \circ (\tau \circ \sigma)$. This can be understood through the following commutative diagram:

% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAC0B9ARhAF9S6TLnyEUAJnJVajFmy4BmfoJAZseAkW6lu0+s1aIQAQX7SYUAObwioAGYAnCAFskZEDghJJMg2zs8INQMdABGMAwACsIaYiAOWJYAFjjK9k6uiNoeXog++nJGAUoC6S5u1J5I2QWGIAA69Th0TI0AxlgObY3Yls50ZnxAA
\begin{tikzcd}
Z_1 \arrow[rd, "f_1"'] \arrow[rr, "\tau \circ \sigma"] &   & Z_3 \arrow[ld, "f_3"] \\
                                                       & A &                      
\end{tikzcd}

Which commutes, because we have:

$$
\begin{align}
	f_1 &=&  f_2             \circ \sigma  \\
		&=& (f_3 \circ \tau) \circ \sigma  \\
		&=&  f_3 \circ (\tau \circ \sigma)
\end{align}
$$

Thus, we have a working composition of morphisms.

3.7.1.c) Associativity

We take 4 objects of the slice category ($f_1 \in (Z_1 \to A)$, $f_2 \in (Z_2 \to A)$, $f_3 \in (Z_3 \to A)$ and  $f_4 \in (Z_4 \to A)$), and three morphisms ($\sigma_A$ mapping $f_1$ to $f_2$, $\tau_A$ mapping $f_2$ to $f_3$, and $\upsilon_A$ mapping $f_3$ to $f_4$). Using composition defined as above, we have

$$
f_1 = f_4 \circ ( \upsilon \circ (\tau  \circ \sigma))
	= f_4 \circ ((\upsilon \circ  \tau) \circ \sigma )
\Rightarrow
  \upsilon_A \circ (\tau_A  \circ \sigma_A)
= (\upsilon_A \circ  \tau_A) \circ \sigma_A
$$
Through associativity in $\mathcal{C}$.


3.7.2) Coslice categories

