\chapter*{Chapter 1, Section 3}

\section*{Example summary}

\begin{itemize}
	\item (3.2): Set, category of sets as objects and set functions as morphisms.
	\item (3.3): preorder (or order, or equivalence relation) over a (single) set, transformed into a category; elements of the set as objects, and elements of the preorder (which is a relation, hence a subset of the cartesian product) as morphisms.
	\item (3.4): the powerset with the inclusion operator, transformed into a category; elements of the powerset (i.e., subsets of the set) as objects, and inclusion relations as morphisms (this is just an example of a preorder / order / equivalence category seen in 3.3).
	\item (3.5): slice categories $\mathcal{C}_A$, categories which isolate a specific object $A$ of a given category $\mathcal{C}$, and studies the morphisms into that object; an object of $\mathcal{C}_A$ is any morphism from any arbitrary objet $Z$ into $A$ (not the homset $Hom(Z, A)$ itself !) and a morphism in $\mathcal{C}_A$ (from $z_1 \in Z_1 \to A$ to $z_2 \in Z_2 \to A$) is a "raising" $\sigma_A$ into $\mathcal{C}_A$ of a morphism $\sigma \in Z_1 \to Z_2$ in $\mathcal{C}$ that preserves composition on morphisms in $\mathcal{C}$ (i.e., $z_1 = z_2 \sigma \Rightarrow \sigma_A z_1 = z_2$).
	\item (3.6): combining examples 3.3 and 3.5, first start with an order category on the set $\mathbb{Z}$ (there is a morphism $m \to n$ iff $m \leq n$), then select a specific object (here, $A = 3$) then study all morphisms of the category into $A$ (so the relation $n \leq 3$ for any $Z = n$); the morphisms $\sigma_3 = (m, 3) \to (n, 3)$ are then simply given by the transitivity of $\leq$, i.e., $m \leq n \leq 3$ ($(m, 3) \to (n, 3)$ corresponds to $m \leq 3 \Rightarrow n \leq 3$, meaning our $z_1 = z_2 \sigma$ transforming into $\sigma_A z_1 = z_2$, here, corresponds to $(m \leq 3) = (n \leq 3) \cap (m \leq n)$ is transformed into $(m \leq 3 \Rightarrow n \leq 3) \cap (m \leq 3) \Leftrightarrow (n \leq 3)$).
	\item (3.7): coslice categories (morphisms out of a chosen object).
	\item (3.8): the category \textbf{Set$^\star$} of pointed sets, a coslice category over \textbf{Set} and any singleton set $\{ \star \}$. Objects in \textbf{Set$^\star$} are regular sets, but with a unique distinguished element; morphisms are any set functions that map the domain's distinguised element to the codomain's distinguished element.
	\item (3.9): "bislice" and "bicoslice" categories, basically a similar construct as slice and coslice, but taking two objects of the starting category, and studying pairs of morphisms (from a common domain, resp codomain) into (resp from) this pair.
	\item (3.10): "fibered bislice" and "fibered bicoslice" categories, once again a similair construct, but this time taking two \textit{morphisms} into a common set C (resp. from a common set C).
\end{itemize}



\section*{On terminal and initial objects in \textbf{Set}}

If $\empty$ is initial and $\{ \star \}$ is terminal, it is because a function in $Set$ (in categorical terms) must always have an output for every input. Ie, in category theory, all functions are maps ("applications").

Said algebraically:

$$
\forall A, B \in \text{Obj}(\bold{Set}), \;
\forall a \in A, \;
\forall f \in \text{Hom}(A, B), \;
\exists f(a) \in B
$$

In the case of $\empty$ as the input set, and there is only one function $f: \empty \to Z$ for any $Z$: $f$ is the empty mapping. But any $Z \to \empty$ (expept $\empty \to \empty$) contains no mapping (since we'd necessarily be ignoring at least one element of $Z$).

Similarly, in the case of the (unique up-to-isomorphism) singleton set $\{ \star \}$ as the output, you'd have multiple functions (precisely $2^{|Z|}$) into it, if you could ignore some elements of the input set. However, if all elements of the input set are required, that leaves you with only one function possible from $Z \to \{ \star \}$: the function which maps all elements to $\star$.




\section*{Restrictions and extensions of functions, and its consequences on a function's nature}

8 possibilities to study, based on the following binary dichotomies:
\begin{itemize}
	\item injection or surjection
	\item enlarging or restricting
	\item domain or codomain
\end{itemize}

Note that enlarging the domain sometimes implies enlarging the codomain, and restricting the codomain sometimes implies restricting the domain.

Legend: Yes, No, Depends

\begin{tabular}{c c c c c}
			& enlarge dom	& restrict dom	& enlarge cod	& restrict cod \\
injection	& D				& Y				& Y				& Y            \\
surjection	& Y				& D				& N				& Y
\end{tabular}


Theorems:

A) if $f \in (A \to B), f \text{ injective (resp. surjective)}$, then $\forall Z \subseteq B, \hat{f} \in ((f^{-1}(Z) \subseteq A) \to Z), \hat{f} = f|_{f^{-1}(Z)}$, the restriction of the function to the corresponding smaller codomain, is also an injection (resp. surjection).

B) if $f \in (A \to B), f \text{ injective (resp. surjective)}$, then $\forall Z \supseteq B, \hat{f} \in (A \to Z), \hat{f} = \iota \circ f$ (with the $\iota$ the canonical injection of $b \in B$ into its superset $Z$), is also an injection (resp. is never a surjection).

C) if $f \in (A \to B), f \text{ injective}$, then $\forall Z \subseteq A, \hat{f} \in (Z \to B), f = \iota_{(Z \to A)} \circ \hat{f}$, we have that $\hat{f}$ is also an injection. However, one can construct $Z \subseteq A$ such that $f$ stops being a surjection.

D) if $f \in (A \to B), f \text{ surjective}$, then $\forall Z \supseteq A, \hat{f} \in (Z \to (B \cup f(Z))), f = \iota_{(Z \to A)} \circ \hat{f}$, we have that $\hat{f}$ is also a surjection. However, one can construct $Z \subseteq A$ such that $f$ stops being a injection.

Proof: TODO





\section*{On the morphisms of slice and coslice categories}

Given a base category $\mathcal{C}$, and some set $A$ we wish to study the homsets of the slice (resp. coslice) category $\mathcal{C}_A$ (resp. $\mathcal{C}^A$. \textbf{These homsets might be empty, or have more than one element.}

We remind that slice categories consider \textit{morphisms to A} as their \textit{objects} (written as $(Z, \varphi)$ for any $\varphi : Z \to A$), while coslice categories consider \textit{morphisms from A} as their \textit{objects} (written as $(\varphi, Z)$ for any $\varphi : A \to Z$. \textit{Morphisms}, of the form $\sigma_A : (Z_1, \varphi_1) \to (Z_2, \varphi_2)$ (resp. $\sigma^A : (\varphi_1, Z_1) \to (\varphi_2, Z_2)$) in a slice category $\mathcal{C}_A$ (resp. coslice category $\mathcal{C}^A$) map such objects to one another if and only if there exists a morphism in $\mathcal{C}$ (the base category!) such that $\varphi_1 = \varphi_2 \sigma$ (resp. $\sigma \varphi_1 = \varphi_2$).


\subsection*{Example of no $\sigma$ for a slice category}

For example, note that there exist pairs of morphisms $f_1 \in (Z_1 \to A)$ and $f_2 \in (Z_2 \to A)$ between which there is no morphism that exists in the slice category. One such example we can make is in $(Vect_\mathbb{R})_{\mathbb{R}^2}$. If we take the maps:

$$f_1 = \begin{bmatrix} 1 & 0 \\ 0 & 0 \end{bmatrix} \in \mathcal{L}(\mathbb{R}^2)$$
$$f_2 = \begin{bmatrix} 0 & 0 \\ 0 & 1 \end{bmatrix} \in \mathcal{L}(\mathbb{R}^2)$$

There exists no map $\sigma$ such that the following diagram commutes (since the output of $f_1$ will always be null in its second coordinate, and the output of $f_2$ will always be null in the first):

% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12BbOnACwBGA4ACUAvgD0ATCDGl0mXPkIoAjOSq1GLNpx78hoyTLkLseAkTKrN9Zq0QduvQcPHTZmmFADm8IqAAZgBOEFxIZCA4EEhS1HY6joEA+qog1Ax0AjAMAAqKFiogwVg+fDiy8iAhYUjqUTGIcVr2bCkmVTXhiJHRdfHaDk7YPjyeYkA
\begin{tikzcd}
\mathbb{R}^2 \arrow[d, "f_1"'] \arrow[r, "\sigma"] & \mathbb{R}^2 \arrow[ld, "f_2"] \\
\mathbb{R}^2                                       &                               
\end{tikzcd}


\subsection*{Example of no $\sigma$ for a coslice category}

TODO add potato diagram

Take $A = Z_2 = \{ a, b, c \}$, $\varphi_2 = id_A$, and $Z_1 = \{ 1, 2 \}$. Since $|Z_1| = |dom(\sigma)| < |cod(\sigma)| = |Z_2|$, there is no possible case in which $\text{Im} (\sigma) = \text{Im} (id_A)$ (even if $\varphi_1$ is epi).


\subsection*{Example of multiple $\sigma$}

TODO add potato diagram

Another example, this time in a coslice category, with $A = \{ a, b, c \}$, we take $\text{\textbf{Set}}_A$. We take $Z_1 = \{ 1, 2, 3 \}$, $Z_2 = \{T, F\}$. For $\varphi_1 : A \to Z_1 = \{(a, 1), (b, 1), (c, 3)\}$ and $\varphi_2 : A \to Z_2 = \{(a, T), (b, T), (c, F)\}$ there exists two elements in $Hom_{\mathcal{Set}^A} (Z_1, Z_2)$. These originate from two functions in \textbf{Set}: $\sigma_\alpha = \{ (1, T), (2, T), (3, F) \}$ and $\sigma_\beta = \{ (1, T), (2, F), (3, F) \}$. The free element in $2 \in Z_1$ which is not in $\text{Im} (\varphi_1)$ offers a degree of freedom.


\subsection*{Explanations on the conditions for $\sigma$}

In the first example, what causes the issue is the fact that the images of $f_1$ and $f_2$ in $A$ are distinct.

In the second example, what causes the issue is the fact that we've reduced our common domain $A$ to an insufficient intermediary object $Z_1$. 

The "element which isn't mapped to offers a degree of freedom and thus breaks unicity" in the last example should remind you of the notes on surjections. Indeed, when comparing $\sigma_\alpha$ and $\sigma_\beta$, we're in a context which is reminiscent of the definition of an epimorphism.

$$\varphi_2 = \sigma_\alpha \varphi_1 = \sigma_\alpha \varphi_1 $$

We can be assured of being able to cancel $\varphi 1$ iff $\varphi_1$ is an epimorphism, and thus $\sigma$, if it exists, is unique. The proof for slice categories is similar, but given the reverse orders, uses monomorphisms.

More generally: 

\begin{itemize}
	\item a) in a slice category, there will be no $\sigma$ if $\text{Im} (\varphi_1) \neq \text{Im} (\varphi_2)$ (proof ? and in more general categories than concrete categories ? TODO: iff ?)
	\item b) in a coslice category, there will be no $\sigma$ if $\text{Pr} (\text{Im} (\varphi_1) \neq \text{Pr} (\text{Im} (\varphi_2))$ (proof ? and in more general categories than concrete categories ? TODO: iff ?)
	\item c) in a slice category, there is at most a single $\sigma$ iff $\varphi_2$ is mono
	\item d) in a coslice category, there is at most a single $\sigma$ iff $\varphi_1$ is epi
\end{itemize}

(see perhaps https://ncatlab.org/nlab/show/over+category and https://ncatlab.org/nlab/show/under+category )